\section{Ethics}

\subsection{Applications and Use-cases}
Consensus algorithms on embedded systems are often used in critical scenarios, such as in the real-time control of multi-agent systems \cite{ConsensusClassDiscretetime, Olfati_Saber_Fax_Murray_2007}. However, they may also find applications in less time-critical scenarios such as charge scheduling in Unmanned Aerial Vehicle (UAVs) \cite{hassijaSchedulingDroneCharging2020}. Using a system unsuited for real-time response and minimal latency in critical applications may lead to catastrophic, yet avoidable failures. In the ideally successful completion of this project, our software library will be published with a permissible license and be modular enough for various implementations. As a result, we have a responsibility to provide a comprehensive analysis of the capabilities of our tool. \textit{For this concern, we will outline the limitations of our system by providing the results of the tests we use to evaluate the library.}

\subsection{Hardware and E-waste}
We will be producing a Printed Circuit Board (PCB) to demonstrate our software library and its use on mobile nodes. However, there exists a valid concern of generating electronic waste by designing a board that will not be reused in the future. Designing circuit boards for short life spans is a wasteful activity that contributes to the unhealthy consumer relationship with electronics where rapid turnover is encouraged due to affordability. \textit{For this concern, we will design a more general development board with the potential to be reused in future projects for prototyping and similar demonstration purposes.}